Efficient forwards-time simulation with ancestral recombination graphs

### 2017-11-03 forwards_paper.tex
Initial draft of WF trees + updated algorithm.

\algstep{W1.}{Initialisation.}{
 For $0 \leq j < N$, set $P_j \leftarrow j$ and $\tau_j \leftarrow T$.
Set $E\leftarrow \emptyset$ and $n \leftarrow N$.
}

\algstep{W2.}{Generation loop.}{ If $t = 0$ terminate.
Set $t \leftarrow t - 1$ and $j \leftarrow 0$.
}

@@

\algstep{W4.}{Mortality.}{ If $\randomuniform([0, 1)) > \delta$, set $P'_j \leftarrow P_j$
    and go to \algref{W7}.
}

@@

\algstep{W8.}{Loop tail}{Set $j \leftarrow j + 1$ and go to \algref{W4}.
}

@@

>>>>

\algstep{W1.}{Initialisation.}{
 For $0 \leq j < N$, set $P_j \leftarrow j$ and $\tau_j \leftarrow T$.
Set $E\leftarrow \emptyset$, $t \leftarrow T$ and $n \leftarrow N$.
}

\algstep{W2.}{Generation loop.}{ If $t = 0$ terminate.
Set $P'_j \leftarrow P_j$ for $0\leq j < N$ and then set $t \leftarrow t - 1$ and $j \leftarrow 0$.
}

@@

\algstep{W4.}{Mortality.}{ If $\randomuniform([0, 1)) \geq \delta$ go to \algref{W8}.
}

@@

\algstep{W8.}{Loop tail}{Set $j \leftarrow j + 1$ and go to \algref{W3}.
}

@@

\begin{figure}
    \begin{center}
        \includegraphics{wf-before}
        \includegraphics{wf-after}
    \end{center}
    \caption{\label{fig:wf-trees}
    }
\end{figure}
